Clustering time series based on probability distributions across temporal granularities

### 2021-11-18 main.Rmd
wpd solution summary plot update - still need to reduce font

@@

In summary, none of the methods captured the five original prototypes exactly. JS-NQT was almost identical, though, but WPD produced quite a different grouping. This is quite a reasonable result and illustrates both the difficulties of clustering to obtain a particularly expected grouping and the ability to learn unexpected patterns in the data. It is possible that the JS-based distances were distracted by the presence of nuisance variables, levels of the granularities, that do not contribute to clustering. This would also be supported by the results of the validation study, where clustering was less effective in S2 and S3, where only some granularities had differences between levels. Clustering using WPD is expected to produce quite different results because it will group only by overall value of a granularity, not a particular pattern. A cluster summarization like Figure \ref{fig:groups-4and5} is not possible because there may be different but equally interesting patterns (e.g. high evening $hod$ and high day time $hod$) in the same cluster. Simply it provides information that across a collection of customers this specific cluster has interesting patterns in a granularity (eg $hod$). One would need to post-process the cluster to separate specific patterns. XXX Might still need some work to summarise the application section

>>>>

```{r opt_clusters-wpd}
```

```{r summary-group-wpd}
```

```{r summary-table-wpd}

```{r summary-plot-wpd, fig.cap = "fill this up", fig.height=6}
```

@@

In summary, none of the methods captured the five original prototypes exactly. JS-NQT was almost identical, though, but WPD produced quite a different grouping. This is quite a reasonable result and illustrates both the difficulties of clustering to obtain a particularly expected grouping and the ability to learn unexpected patterns in the data. It is possible that the JS-based distances were distracted by the presence of nuisance variables, levels of the granularities, that do not contribute to clustering. This would also be supported by the results of the validation study, where clustering was less effective in S2 and S3, where only some granularities had differences between levels. Clustering using WPD is expected to produce quite different results because it will group only by overall value of a granularity, not a particular pattern. A cluster summary like Figure \ref{fig:groups-4and5} is not possible because there may be different but equally interesting patterns (e.g. high evening $hod$ and high day time $hod$) in the same cluster. Simply it provides information that across a collection of customers this specific cluster has interesting patterns in a granularity (eg $hod$). One would need to post-process the cluster to separate specific patterns. XXX Might still need some work to summarise the application section
